On the Minimum Core Mass for Giant Planet Formation at Wide Separations

### 2013-10-29 tex/draft/draft4.tex
added Rafikov discussion

>>>>

\subsection{Planetesimal Accretion}
\label{sec:placc}

Our regime assumes that the protoplanetary core is fully grown and planetesimal accretion has ceased. However, it is possible, in theory, for the atmosphere to reach crossover and initiate runaway gas accretion during core growth, i.e. before planetesimal accretion becomes low enough for KH contraction to start dominating. This concern is explored in detail in Piso et al. (in prep.), where we compare our results to the static model of R06. We find that our model yields lower critical core masses than the R06 corresponding study for large planetesimal accretion rates. It follows that the accretion of solids can be safely ignored in our regime, and that giant planet formation is faster with variable planetesimal accretion rates.

%an additional concern for our regime is whether the atmosphere becomes critical before KH contraction starts dominating, i.e. the atmosphere may reach crossover before planetesimal accretion slows down to the maximum rate imposed by our model, which satisfies L_KH = L_acc
